% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{book} % use larger type; default would be 10pt

\input{header.inc}

\geometry{letterpaper,outer=0.5in,inner=0.5in,top=1in,bottom=0.5in}
\setcounter{page}{94}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\LARGE\fontspec[Ligatures=TeX]{Garamond Premier Pro}\textbf{\thepage}}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\garamondbig
\vspace*{-0.5in}
\printsmalltitle{O Magnum Mysterium}

\greannotation{Resp.}
\greannotation{3.}
\gregorioscore{94_re--o_magnum_mysterium--solesmes}

\large
Translation from CPDL:

\noindent\emph{O great mystery and wonderful sacrament, that animals should see the new-born Lord lying in a manger!\\
Blessed is the Virgin, whose womb was worthy to bear Christ the Lord.\\
\Vbar{}.~Hail Mary, full of grace: the Lord is with you.\\
Blessed is the Virgin, whose womb was worthy to bear Christ the Lord.}

\pagebreak
\LARGE
\hbox{}\newpage

\printsmalltitle{Lucis Creator \#2}

\greannotation{Hymn.}
\greannotation{8.}
\gregorioscore{96_hy--lucis_creator_optime_(another_chant_ad_libitum)--solesmes}

\bigskip
Translation from preces-Latinae.org:

\newcommand{\iteme}[1]{
	\item\emph{#1}
}

\newcounter{vcounter}
\begin{list}{\arabic{vcounter}.}{\usecounter{vcounter}}
\iteme{O Blest Creator of the light, / Who mak'st the day with radiance bright, / and o'er the forming world didst call / the light from chaos first of all;}
\iteme{Whose wisdom joined in meet array / the morn and eve, and named them Day: / night comes with all its darkling fears; / regard Thy people's prayers and tears.}
\iteme{Lest, sunk in sin, and whelmed with strife, / they lose the gift of endless life; / while thinking but the thoughts of time, / they weave new chains of woe and crime.}
\iteme{But grant them grace that they may strain / the heavenly gate and prize to gain: / each harmful lure aside to cast, / and purge away each error past.}
\iteme{O Father, that we ask be done, / through Jesus Christ, Thine only Son; / Who, with the Holy Ghost and Thee, / doth live and reign eternally. Amen.}
\end{list}
\pagebreak

\printsmalltitle{O Filii et Filiæ}

\LARGE
%\grechangestaffsize{23}
\greannotation{Hymn.}
\greannotation{2.}
\gregorioscore{98_hy--o_filii_et_filiae--solesmes}

\large
Translation from preces-Latinae.org:

\begin{list}{\arabic{vcounter}.}{\usecounter{vcounter}\setlength\parsep{0pt}}
\iteme{Ye sons and daughters of the Lord, / the King of glory, King adored, / this day Himself from death restored.}
\iteme{All in the early morning gray / went holy women on their way, / to see the tomb where Jesus lay.}
\iteme{Of spices pure a precious store / in their pure hands these women bore, / to anoint the sacred Body o'er.}
\iteme{The straightaway one in white they see, / who saith, ``seek the Lord: but He / is risen and gone to Galilee.''}
\iteme{This told they Peter, told John; / who forthwith to the tomb are gone, / but Peter is by John outrun.}
\iteme{That self-same night, while out of fear / the doors where shut, their Lord most dear / to His Apostles did appear.}
\end{list}


\end{document}